SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-16 MDPI/sensors-1915564/template.tex
Update Paper Review 1.7

% Authors, for the paper (add full first names)
\Author{Viet Dung Nguyen $^{1,\dagger, *}$\orcidA{}, Ngoc Dung Bui $^{2,\dagger}$\orcidB and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}

@@

% Contact information of the corresponding author
\corres{Correspondence: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (N.V.D.)}

>>>>

% Authors, for the paper (add full first names)
\Author{Viet Dung Nguyen $^{1,\dagger, *}$\orcidA{}, Ngoc Dung Bui $^{2, *}$\orcidB{} and Hoang Khoi Do  $^{1,\dagger}$\orcidC{}}

@@

% Contact information of the corresponding author
\corres{Correspondences: dung.nguyenviet1@hust.edu.vn; Tel.:  +84-9834-443-22 (N.V.D.), dnbui@utc.edu.vn; Tel: +84-9130-451-30 (N.D.B.)}
